%------------------------
% Resume Template
% Author : Rishabh Verma
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\def\Plus{\texttt{+}}
\def\Minus{\texttt{-}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Rishabh Verma}} & Email: \href{mailto:rishabhverma17@gmail.com}{rishabhverma17@gmail.com}\\
  \href{https://www.linkedin.com/in/rishabhverma17}{LinkedIn: linkedin.com/in/rishabhverma17} & Mobile:~~~+91-995-8783-667 \\
  \href{https://github.com/rishabhverma17}{Github: ~~github.com/rishabhverma17} & Web:
  \href{https://resume.rishabhverma.in/}{resume.rishabhverma.in}\\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Summary}
  \resumeSubHeadingListStart
\resumeItemWithoutTitle{}{Problem solver with experience in developing low latency, highly scalable, fault-tolerant, distributed backend services and evolving the architecture for performance and scalability. Experience of Object-Oriented Programming, Object-Oriented Design, Messaging, Event Streaming, Data Structures and Algorithms, Prevalent Design Patterns, Caching, NoSQL, RDBMS.}
\resumeSubHeadingListEnd
\section{Technical Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Tech Stack}{Java 8, SpringBoot, Azure, C\#, MySQL, Cassandra, MongoDB, Aerospike, RESTful API's, Kafka, Microservices, Data Structures, Algorithms, Agile Development, Elasticsearch, Logstash}
	\vspace{2pt}
	\resumeSubItem{Tools}{GIT, Jenkins, Maven, Gradle, Kubernetes, Docker, Pinpoint, Icinga, Grafana, Kibana}

\resumeSubHeadingListEnd
\vspace{-2pt}
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading{Microsoft}{Noida, India}
    {Software Development Engineer II}{May 2022 - Present}
    \resumeItemListStart
          \resumeItem{Working in C\Plus E PSX SPARK DEV Team}
          \newline
      \resumeItemListEnd
  \resumeSubheading
		{Snapdeal (Snapdeal.com)}{Gurgaon, India}
		{Software Development Engineer II}{Mar 2021 - May 2022}
		%\newline\newline
    \vspace{-6pt}
    %\textbf{Developing low latency and highly scalable distributed backend services for Buyers Platform.}
		\resumeItemListStart
        \resumeItem{Buyers Platform}
          {My team owns services like Checkout, Cart Service, Post Order Management, Order Payment Management Service, Order Management Service, Promotions, Payments and API aggregator service.}
        \resumeItem {Snapdeal Pro Subscription} {Designing a new service which is a subscription based system. Users can buy different plans available to avail more discounts and better offers than other non pro users.}
        \resumeItem {Reward \& Referral System} {Successfully designed and deployed a new Referral and Reward service from scratch. My ownership includes designing the systems high level design, low level design, implementation of services and moving system to production. Initial stats shows 63,000+(Daily Avg) new and returning users signed up for this program. Which directly impacted sales and customer retention.}
        \newline
		\resumeItemListEnd
\vspace{2pt}
    \resumeSubheading{Yatra Online Pvt Ltd (Yatra.com)}{Bangalore, India}
    {Software Development Engineer}{Jan 2020 - Feb 2021}
    %\newline\newline
    %\vspace{-6pt}
    %\textbf{Focused on developing low latency and highly scalable distributed backend services for Yatra Hotels.}
    \resumeItemListStart
          \resumeItem{Build Your Own Package - Holidays Platform}{Building a new Holidays platform at Yatra from scratch in which user can select the destination(s) and date(s) of travel and we would provide them with curated low cost and best star rating package which includes Hotel, Travel(Flight or Intra/Inter state CAB). User can change/replace or update any particular component in the base package from UI making it customizable as per user needs. }
          \resumeItem{Central Logging Pipeline}{Designed a central logger service for external microservices metric logging. This service is made agnostic and easy to integrate with all other microservices.}
          \resumeItem{Auto Suggest}{Created new the de-duplication pipeline for better results.}
          \newline
      \resumeItemListEnd
\vspace{2pt}
    \resumeSubheading
		{Delhi Integrated Multi Modal Transit System (DIMTS)}{New Delhi, India}
		{Software Development Engineer}{Jan 2019 - Jan 2020}
		\resumeItemListStart
        \resumeItem{Designed DMRC and DIMTS Reconciliation System}
          { This System reduced reconciliation time by 70\% and also eliminated manual effort.}
        \resumeItem{Developed Automated Recovery Service}
          {Developed tool for automated recovery of trips and shifts corrupted due to operational issues of ETM machine.}
        \resumeItem{ETM Challan}{Redesigned ETM Challan module so that ETM machines can be moved more than once a day.
        \textbf{Impact:~Reduced ETM Movement cost by 30\%}}
        \vspace{0pt}
        \newline
		\resumeItemListEnd
\vspace{2pt}
    \resumeSubheading{Aperta Limited}{Coimbatore, India}
    {Software Engineer}{Aug 2016 - Jan 2019}
    \resumeItemListStart
          \resumeItem{Developed Interface Utility Bank’s in-house utility which interacts with Core banking system (CBS) and Cheque truncation system (CTS)}{It Reduced the time by 75\% to process 70,000 to 1,00,000 instruments from 16 seconds to less than 4 seconds by redesigning the algorithm.}
          \newline
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Gesture IT (2016)}{A gesture-based hardware control system. With this system we aim to allow the user to control a hardware device using natural gestures wirelessly.}
\vspace{2pt}
\resumeSubItem{Slang Translator (Open Source)}{Python script that takes input from user and finds any abbreviation available in it as described in text file, If found it will replace it with its corresponding phrase.}
\newline
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Education}
  \resumeSubHeadingListStart
	\resumeSubheading
    {Bachelor Of Technology (B.Tech)}
    {Greater Noida, India}{Computer Science and Engineering from Sharda University}
    {2012 - 2016}
\resumeSubHeadingListEnd

\end{document}